
\subsection{\texttt{reduce!} Special Form}
{
	A call to the \texttt{reduce!} special form can be used as an expression.
	The special form expects three parameters.
	The first parameter must be a lambda value, and the
	second parameter must be a list value.
	The lambda value's first parameter's type
	must match the element type of the list value and the type of the third
	parameter. The lambda value's
	second parameter's type must match the lambda value's return type.
	
	The lambda value is called repeatedly, once for each element of the list.
	The lambda is called with the result of the last time it was
	called (initially the third parameter), and
	the current element.
	
	If Guardian can determine the exact lambda and list value used in a call to
	\texttt{reduce!}, Guardian will replace the call with a literal of
	the appropriate value.
	
	\begin{itemize}
	{
		\item \texttt{reduce!(\$int x, y -> int: x + y, [1, 2, 3], 0)}]
		
			First the lambda is called with 0 and 1 yielding 1.
			Then the lambda is called with 1 and 2 yielding 3.
			Then the lambda is called with 3 and 3 yielding 6.
		
		\item \texttt{reduce!(\$int x, y -> int: x > y ? x : y, [2, 3, 1, 4], 0)}]
		
			First the lambda is called with 0 and 2 yielding 2.
			Then the lambda is called with 2 and 3 yielding 3.
			Then the lambda is called with 3 and 1 yielding 3.
			Then the lambda is called with 3 and 4 yielding 4.
		
		\item \texttt{reduce!(\$int x, y -> int: x < y ? x : y, [2, 3, 1, 4], 5)}]
		
			First the lambda is called with 5 and 2 yielding 2.
			Then the lambda is called with 2 and 3 yielding 2.
			Then the lambda is called with 2 and 1 yielding 1.
			Then the lambda is called with 1 and 4 yielding 1.
			
		\item \texttt{reduce!(\$int x, int[] y -> int[]: x \% 2 == 0 ? y + [x] : y, [2, 3, 1, 4], [<int>])}]
		
			First the lambda is called with \texttt{[<int>]} and 2 yielding \texttt{[2]}.
			Then the lambda is called with \texttt{[2]} and 3 yielding \texttt{[2]}.
			Then the lambda is called with \texttt{[2]} and 1 yielding \texttt{[2]}.
			Then the lambda is called with \texttt{[2]} and 4 yielding \texttt{[2, 4]}.
			
		\item \texttt{reduce!(\$int x, y -> int: 1, [<int>], 3)}]
		
			Due to the list consisting of no elements, the third parameter
			is returned.
	}
	\end{itemize}
}













