
\subsection{Inclusion Expression}
{
	Inclusion is a kind of expression that results in a boolean value of
	the result of the first expression ``is inside'' of the result of the
	second expression. Strings, lists, sets and dictionary types are currently
	supported.
	When the \lstinline[language=MAIA, columns=fixed]@in@ operator is done
	on two strings, the boolean value returned
	indicates whether the first string
	is a substring of the second.
	When the \lstinline[language=MAIA, columns=fixed]@in@ operator is done on
	a value and a list/set,
	the boolean value returned indicates whether the first value
	is an element of the list/set.
	When the \lstinline[language=MAIA, columns=fixed]@in@ operator is done on
	a value and a dictionary,
	the boolean value returned indicates whether the first value
	is a key of the dictionary.
	
	If Guardian can determine the exact value of the two given subexpressions,
	Guardian will replace the call with the appropriate boolean literal.
	
	\begin{itemize}
	{
		\item[] \lstinline[language=MAIA, columns=fixed]@"ab" in "abc"@
		
			Results in a true boolean value.
		
		\item[] \lstinline[language=MAIA, columns=fixed]@"ba" in "abc"@
		
			Results in a false boolean value.
		
		\item[] \lstinline[language=MAIA, columns=fixed]@3 in {1, 3, 2, 5}@
		
			Results in a true boolean value.
		
		\item[] \lstinline[language=MAIA, columns=fixed]@4 in {1, 3, 2, 5}@
		
			Results in a false boolean value.
		
		\item[] \lstinline[language=MAIA, columns=fixed]@3 in {1: 10, 3: 30, 2: 20, 5: 50}@
		
			Results in a true boolean value.
		
		\item[] \lstinline[language=MAIA, columns=fixed]@4 in {1: 10, 3: 30, 2: 20, 5: 50}@
		
			Results in a false boolean value.
	}
	\end{itemize}
}
